Verifying Demonstrations

### 2017-09-27 conclusions.tex
Makes minor improvements in disposition of slides
Removes open problems from conclusions
This part was only for FOSAD anyway.

\subsection<presentation>{Related work}

@@

\subsection{Open problems}

\begin{frame}
  \frametitle{Sybil}
  \begin{question}
    How to solve Sybil, can we piggyback on existing \acp{PKI}?
    E.g.\ through~\cite{Cinderella}.
  \end{question}

  \begin{question}
    Can we otherwise bind identifiable keys to unique ring signature keys?
  \end{question}

  \begin{question}
    Can we achieve receipt freeness (deniability) and protect from Sybil?
  \end{question}
\end{frame}

\begin{frame}
  \frametitle{Anonymous communication}
  \begin{question}
    How do we submit the proofs to storage?
  \end{question}

  \mode<presentation>{%
    \begin{remark}
      Without anonymous submission we don't get proof privacy, thus no 
      receipt freeness either.
    \end{remark}
  }
\end{frame}

\begin{frame}
  \frametitle{Blockchains, distributed systems}
  \begin{question}
    \begin{itemize}
      \item Malicious nodes want to provide Alice with a view that her proof is 
        included.
      \item Everyone else is provided a view without Alice.
      \item How can we ensure a consistent view for everyone?
    \end{itemize}
  \end{question}

  \begin{question}
    Can we do blockchain branch and merge?
  \end{question}
\end{frame}

>>>>

\mode<presentation>{%
\subsection{Related work}
}

@@
